Does a fully convective star need a special corona to produce a polar flare?

### 2023-07-20 src/tex/ms.tex
[showyourwork] overleaf sync

\subsection{Spectral fitting: EPIC}
We use XSPEC version 12.12.1~\citep{arnaud1996xspec} to fit a two-temperature additive APEC~\citep{smith2001collisional,foster2012updated} model to the joint PN and MOS spectra, using solar abundances from~\citet{grevesse1998standard}, but adjusting to an Fe/0=.6 ratio, which is more typical of M dwarfs~\citep{wood2018chandra}. We analyzed both the full data set, and the quiescent and flaring parts separately. In the full data set, we used the \texttt{bayes} method in XSPEC to assign constant priors within the model's hard limits, and sample the uncertainties using the Markov-Chain-Monte-Carlo (MCMC) method using \texttt{chain} for a total of 30000 steps, discarding the first 5000 as the burn-in phase. From the same fit, but using PN data only, we derived the flux and X-ray luminosity in the 0.2-12 keV band. For the quiescent and flaring portions of the observations, we chose the same procedure, but chose the Gaussian prior distributions for the two coronal temperatures using the full data set as ground truth, and assigning the largest of the upper and lower uncertainties as standard deviation.

@@

From the PN spectra, we measured a soft X-ray flux of $F_X=XXXX$, and a luminosity $L_X=XXXX$ in the $0.2-2\,$keV band. In the broader $0.2-10\,$keV band, we measured XXXX and XXXX.
 \begin{table}
% \movetableright=-20mm
\centering
    \script{TABLE_specfits.py}
    \caption{XSPEC fits EPIC spectra for different subsets of observations.}
    \input{output/mcmc_specfit.tex}
        \label{tab:specfit}
\end{table}

% \begin{figure}
%     \script{FIGURE_data_resid.py}
%     \begin{centering}
%         \includegraphics[width=\linewidth]{figures/pn_onlyflare_data_resid.png}
%         \caption{
%          Flare only PN Double apec spectrum fit.
%         }
%         \label{fig:spec_pn_onlyflare}
%     \end{centering}
% \end{figure}

% \begin{figure}
%     \script{FIGURE_data_resid.py}
%     \begin{centering}
%         \includegraphics[width=\linewidth]{figures/pn_noflare_data_resid.png}
%         \caption{
%          No flare PN Double apec spectrum fit.
%         }
%         \label{fig:spec_pn_noflare}
%     \end{centering}
% \end{figure}

% \begin{figure}
%     \script{FIGURE_data_resid.py}
%     \begin{centering}
%         \includegraphics[width=\linewidth]{figures/pn_data_resid.png}
%         \caption{
%          PN Double apec spectrum fit.
%         }
%         \label{fig:spec_pn}
%     \end{centering}
% \end{figure}

% \begin{figure}
%     \script{FIGURE_data_resid.py}
%     \begin{centering}
%         \includegraphics[width=\linewidth]{figures/mos1_data_resid.png}
%         \caption{
%          MOS1 Double apec spectrum fit.
%         }
%         \label{fig:spec_mos1}
%     \end{centering}
% \end{figure}

% \begin{figure}
%     \script{FIGURE_data_resid.py}
%     \begin{centering}
%         \includegraphics[width=\linewidth]{figures/mos2_data_resid.png}
%         \caption{
%          MOS2 Double apec spectrum fit.
%         }
%         \label{fig:spec_mos2}
%     \end{centering}
% \end{figure}

% \begin{figure}
%     \script{FIGURE_data_resid.py}
%     \begin{centering}
%         \includegraphics[width=\linewidth]{figures/joint_onlyflare_data_resid.png}
%         \caption{
%          Flare only joint Double APEC spectrum fit.
%         }
%         \label{fig:spec_joint_onlyflare}
%     \end{centering}
% \end{figure}

% \begin{figure}
%     \script{FIGURE_data_resid.py}
%     \begin{centering}
%         \includegraphics[width=\linewidth]{figures/joint_noflare_data_resid.png}
%         \caption{
%          Joint Double APEC spectrum fit with flare excluded.
%         }
%         \label{fig:spec_joint_noflare}
%     \end{centering}
% \end{figure}

% \begin{figure}
%     \script{FIGURE_data_resid.py}
%     \begin{centering}
%         \includegraphics[width=\linewidth]{figures/joint_all_data_resid.png}
%         \caption{
%          Joint Double APEC spectrum fit.
%         }
%         \label{fig:spec_joint_all}
%     \end{centering}
% \end{figure}

\begin{figure}
    \script{FIGURE_data_resid.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/joint_vapec_fe06_data_resid.png}
        \caption{
         Joint Double APEC spectrum fit with Fe/0$=0.6$.
        }
        \label{fig:spec_joint_all}
    \end{centering}
\end{figure}

@@

\begin{table}
% \movetableright=-20mm
\centering
    \script{TABLE_tess_flares.py}
    \caption{Flares detected with TESS. $a$ is the relative amplitude, and $E$ is the bolometric flare energy assuming a 10,000 K blackbody emission from the flare.
    \input{output/tess_flares.tex}
        \label{tab:flares}
\end{table}

@@

A third, very hot, $>40\,$MK component could only be poorly constrained due to a lack of sensitivity to flux above $5\,$keV. DS Tuc A, a young G dwarf, has been observed flaring with a >50 MK temperature in the flare peaks~\citep{pillitteri2022xraya}, and PMS stars can exceed 100 MK~\citep{getman2008xray, getman2021xray}. The Sun can heat the corona up to over 30 MK during flares~\citep{benz2016flare}. A flare on AD Leo had a peak temperature of about 37 MK~\citep{stelzer2022great}. Other M dwarf flares are well-described with two temperatures~\citep{behr2023muscles, magaudda2022firsta}. The corona of NLTT 33370 AB, an M7 binary with a rotation period of about $3.8\,$h (close to TIC 277's $4.56\,$h) is combined of a 3.1 MK and 14 MK component~\citep{williams2015simultaneous}.

\textcolor{red}{the poorly constrained third component could stem from the low energy tail of the hard X-ray emission at >10 keV.}

>>>>

\subsection{Spectral fitting: EPIC}
We use XSPEC version 12.12.1~\citep{arnaud1996xspec} to fit a two-temperature (2T) additive APEC~\citep{smith2001collisional,foster2012updated} model to the joint PN and MOS spectra, using solar abundances from~\citet{grevesse1998standard}, but adjusting to an Fe/0$=0.6$ ratio, which is more typical of M dwarfs~\citep{wood2018chandra}. We analyzed both the full data set, and the quiescent and flaring parts separately. Neither subset could be adequately fit with a single temperature component (1T), and a 3T model did not improve the fit compared to the 2T-model either. In the full data set, we used the \texttt{bayes} method in XSPEC to assign constant priors within the model's hard limits, and sample the uncertainties using the Markov-Chain-Monte-Carlo (MCMC) method using \texttt{chain} for a total of 30000 steps, discarding the first 5000 as the burn-in phase. From the same fit, but using PN data only, we derived the flux and X-ray luminosity in the 0.2-12 keV band. For the quiescent and flaring portions of the observations, we chose the same procedure, but used Gaussian prior distributions for the two coronal temperatures using the full data set as ground truth, and assigning the largest of the upper and lower uncertainties as standard deviation.

@@

From the PN spectra, we measured a soft X-ray flux of $F_X=XXXX$, and a luminosity $L_X=XXXX$ in the $0.2-2\,$keV band. 
 \begin{table}
% \movetableright=-20mm
\centering
    \script{TABLE_specfits.py}
    \caption{XSPEC fits EPIC spectra for different subsets of observations.}
    \input{output/mcmc_specfit.tex}
        \label{tab:specfit}
\end{table}

\begin{figure}
    \script{FIGURE_data_resid.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/joint_chain_fit_data_resid.png}
        \caption{
         Joint Double APEC spectrum fit with Fe/0$=0.6$.
        }
        \label{fig:spec_joint_all}
    \end{centering}
\end{figure}

@@

\begin{table}
% \movetableright=-20mm
\centering
    \script{TABLE_tess_flares.py}
    \caption{Flares detected with TESS. $a$ is the relative amplitude, and $E_{\rm bol}$ is the bolometric flare energy assuming a 10,000 K blackbody emission from the flare.}
    \input{output/tess_flares.tex}
        \label{tab:flares}
\end{table}

@@

A third, very hot, $>40\,$MK component could only be poorly constrained due to a lack of sensitivity to flux above $5\,$keV. DS Tuc A, a young G dwarf, has been observed flaring with a >50 MK temperature in the flare peaks~\citep{pillitteri2022xraya}, and PMS stars can exceed 100 MK~\citep{getman2008xray, getman2021xray}. The Sun can heat the corona up to over 30 MK during flares~\citep{benz2016flare}. A flare on AD Leo had a peak temperature of about 37 MK~\citep{stelzer2022great}. Other M dwarf flares are well-described with two temperatures~\citep{robrade2010quiescent, behr2023muscles, magaudda2022firsta}. The corona of NLTT 33370 AB, an M7 binary with a rotation period of about $3.8\,$h (close to TIC 277's $4.56\,$h) is combined of a 3.1 MK and 14 MK component~\citep{williams2015simultaneous}. However, flares on Proxima Cen (M5.5, 85 d rotation~XXXX), also appear with temperatures of 2-3 MK and 10-20 MK~\citep{gudel2004flares,fuhrmeister2022high, howard2022mouse}.
